\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
re- factored conclusion

 \noindent \emph{Neural recognition models for program induction:} Much recent work in the ML community has
 focused on creating neural networks that regress from
 input/output examples to programs~\cite{devlin2017robustfill,devlin2017neural,menon2013machine,balog2016deepcoder}. This family of work is closest to the lesioned version of
 \system where $(\mathcal{D},\theta)$ is held fixed and $q$ is learned (RF/DC baseline).
 These neural networks are typically trained with strong supervision (i.e., with annotated ground-truth programs) on massive data sets (i.e., hundreds of millions~\cite{devlin2017robustfill}).
 In our work we consider a weakly-supervised setting where ground truth programs are not provided and
 the agent must learn from a few hundred tasks.

@@

 \section{Contribution and Outlook}
 We contributed a model, \systemEnding, that learns to program by
 bootstrapping a DSL with new domain-specific primitives that the algorithm itself discovers.
  Alongside this DSL, we train a bottom-up
 neural recognition model that learns how to efficiently deploy the
 DSL and hone in on the right programs.
 %% We believe that this
 %% integration of top-down symbolic representation and bottom-up neural
 %% networks -- both of them learned -- is a useful general approach for
 %% getting program induction off the ground. 
Many directions remain open for future work. Two immediate goals are to
integrate more sophisticated neural recognition models~\cite{devlin2017robustfill} and
program synthesizers~\cite{solar2008program}, which may improve performance in some
domains over the simple, generic methods used here, and to explore DSL
meta-learning: Can we find a single universal primitive set that could
effectively bootstrap DSLs for new domains, including the four domains
considered but many others?

>>>>

 \noindent \emph{Deep Learning:} Much recent work in the ML community has
 focused on creating neural networks that regress from
 input/output examples to programs~\cite{devlin2017robustfill,devlin2017neural,menon2013machine,balog2016deepcoder}. %This family of work is closest to our RF/DC baseline.
 These neural networks are typically trained with strong supervision (i.e., with annotated ground-truth programs) on massive data sets (i.e., hundreds of millions~\cite{devlin2017robustfill}).
 Our work  considers a weakly-supervised regime where ground truth programs are not provided and
 the agent must learn from a few hundred tasks.

@@

 \section{Contribution and Outlook}
 We contribute a model, \systemEnding, that learns to program by
 bootstrapping a DSL with new domain-specific primitives that the algorithm itself discovers.
  Alongside this DSL, we train a bottom-up
 neural recognition model that learns how to efficiently deploy the
 DSL and hone in on the right programs.
 We believe that this
 integration of top-down symbolic representation and bottom-up neural
 networks -- both of them learned -- is a useful general approach for
 program induction.
Many directions remain open for future work. Two immediate goals are to
integrate more sophisticated neural recognition models~\cite{devlin2017robustfill} and
program synthesizers~\cite{solar2008program}, which may improve performance in some
domains over the generic methods used here, and to explore DSL
meta-learning: Can we find a single universal primitive set that could
effectively bootstrap DSLs for new domains, including the four domains
considered but also many others?
